Demo arXiv template

### 2022-11-23 paper/paper.qmd
updates after meeting

**Raw data**

@@

<!-- The location $s$ can refer to vector points or areas characterised by longitude-latitude coordinates, or raster cells obtained from satellite images. -->

<!-- The time dimension $t$ can be daily, weekly, biweekly (14-16 days), monthly, or even quarterly -->

<!-- Variables -->

<!-- This multidimensional array structure is commonly used in geospatial analysis -->

<!-- Given the variety of data sources at different spatial resolution and temporal granularity, the raw data may first come in multiple pieces.  -->
<!-- Sometimes, even a considerable amount of work is needed to align the spatial and temporal extent of multivariate data. -->

@@

 <!-- - $\theta$ can be a constant or a derived from the data -->

@@

While scaling can be seen as a specific type of variable tranformation, it is separated into own step to make the scaling operation explicit in the pipeline.
The key difference between the two steps is that variable transformation typically changes the shape of the data while scaling only changes the data scale and can usually be written in the form of $$[x(s_i;t_j) - \alpha]/\gamma.$$
For example, A z-score standardisation can be written in the above form with $\alpha = \bar{x}(s; t)$ and $\gamma = \sigma(s; t)$, a min-max standardisation uses $\alpha = \min[x(s_i, t_j)]$ and $\gamma = \max[x(s_i, t_j)] - \min[x(s_i, t_j)]$.
@fig-scale-var-trans-compare shows a collection of variable pre-processing operations and uses color to differentiate whether the operation is a variable transformation or a scaling step. All the scaling operations in green results in the same shape as the original data.

@@

@@

<!-- specifically for converting from a fitted distribution to normal score via reverse CDF function, non-parametric formula, or empirical approximation, a common step in many index: SPI, SSI, Z score. The purpose of normalising is to convert the index into a standardised series after all the steps for the ease of comparison. -->

>>>>

**Notation**

@@

  <!-- * all the different choice in each step will affect the final index series ot make decision, i.e. $k$ in temporal aggregation, to assess drought in different scale: short-term, mid-term, long-term. -->

@@

@@

While scaling can be seen as a specific type of variable tranformation, it is separated into own step to make the scaling operation explicit in the pipeline.
The key difference between the two steps is that variable transformation typically changes the shape of the data while scaling only changes the data scale and can usually be written in the form of $$[x(s_i;t_j) - \alpha]/\gamma.$$
For example, a z-score standardisation can be written in the above form with $\alpha = \bar{x}(s; t)$ and $\gamma = \sigma(s; t)$, a min-max standardisation uses $\alpha = \min[x(s_i, t_j)]$ and $\gamma = \max[x(s_i, t_j)] - \min[x(s_i, t_j)]$.
@fig-scale-var-trans-compare shows a collection of variable pre-processing operations and uses color to differentiate whether the operation is a variable transformation or a scaling step. All the scaling operations in green results in the same shape as the original data.

@@

**Distribution fit**

$$F_{\eta}(x(\mathbf{s}; \mathbf{t}))$$

@@

### 2022-11-23 paper/paper.tex
updates after meeting

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, frame hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced, breakable, sharp corners, interior hidden]}{\end{tcolorbox}}\fi

@@

\textbf{Raw data}

@@

While scaling can be seen as a specific type of variable tranformation,
it is separated into own step to make the scaling operation explicit in
the pipeline. The key difference between the two steps is that variable
transformation typically changes the shape of the data while scaling
only changes the data scale and can usually be written in the form of
\[[x(s_i;t_j) - \alpha]/\gamma.\] For example, A z-score standardisation
can be written in the above form with \(\alpha = \bar{x}(s; t)\) and
\(\gamma = \sigma(s; t)\), a min-max standardisation uses
\(\alpha = \min[x(s_i, t_j)]\) and
\(\gamma = \max[x(s_i, t_j)] - \min[x(s_i, t_j)]\).
Figure~\ref{fig-scale-var-trans-compare} shows a collection of variable
pre-processing operations and uses color to differentiate whether the
operation is a variable transformation or a scaling step. All the
scaling operations in green results in the same shape as the original
data.

@@

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, boxrule=0pt, interior hidden, breakable, borderline west={3pt}{0pt}{shadecolor}, sharp corners, frame hidden]}{\end{tcolorbox}}\fi

@@

\textbf{Notation}

@@

While scaling can be seen as a specific type of variable tranformation,
it is separated into own step to make the scaling operation explicit in
the pipeline. The key difference between the two steps is that variable
transformation typically changes the shape of the data while scaling
only changes the data scale and can usually be written in the form of
\[[x(s_i;t_j) - \alpha]/\gamma.\] For example, a z-score standardisation
can be written in the above form with \(\alpha = \bar{x}(s; t)\) and
\(\gamma = \sigma(s; t)\), a min-max standardisation uses
\(\alpha = \min[x(s_i, t_j)]\) and
\(\gamma = \max[x(s_i, t_j)] - \min[x(s_i, t_j)]\).
Figure~\ref{fig-scale-var-trans-compare} shows a collection of variable
pre-processing operations and uses color to differentiate whether the
operation is a variable transformation or a scaling step. All the
scaling operations in green results in the same shape as the original
data.

@@

\textbf{Distribution fit}

\[F_{\eta}(x(\mathbf{s}; \mathbf{t}))\]
